---
title: "AE 20: a dataset's life"
---

```{r}
#| message: false
library(tidyverse)
library(tidymodels)
```

If you are like me, you are sick of the penguins at this point. So for our last act, let's banish them to worlds beyond. I packed all of those lil' beasts onto a rocket ship and took them to both Mars and Venus, where I recorded their weights (in pounds). I then abandoned the ship to hurtle through space so that future stawanana students never have to study them again. 

# Preparation 

## Load the data 

I have two sets of measurements for the same sample of penguins: one set taken on Mars, and another on Venus. They are contained in two separate files that need to be merged:

```{r}
#| message: false
penguins_venus <- read_csv("data/penguins_venus.csv")
penguins_mars <- read_csv("data/penguins_mars.csv")
```

## Merge the data 

**Task**: Use an appropriate `join` function to create a new data frame called `space_penguins`:

```{r}
# add code
```

## Reshape the data 

**Task**: Use an appropriate `pivot` function to create a new version of `space_penguins` where the information on the planet where the measurements were taken is its own column:

```{r}
# add code
```


# Exploration 

## Pictures

**Task**: Generate side-by-side density plots of the weights on each planet.


```{r}
# add code
```

## A concise set of numerical summaries

**Task**: compute the mean, standard deviation, and median of weight on each planet:


```{r}
# add code
```

# Modeling 

What is the conversion factor between weights on venus and weights on mars? If you ask a physicist, I'm pretty sure they will tell you it's this:

$$
mars~weight~(lb)\approx venus~weight~(lb)\times 0.41.
$$

So, you weigh less on Mars than you do on Venus. If we didn't already know this, could we learn it from our data? Note that is is not a foregone conclusion, because our data are *noisy*. The weights have been measured *with error*, and so what should be a perfect straight line relationship won't be, exactly.

## Linear 

**Task**: Create a scatterplot of Venus weights versus Mars weights, and add a line of best fit:


```{r}
# add code
```

**Task**: Compute the estimated slope and intercept of the best fit line:


```{r}
# add code
```


## Logistic

**Task**: fit a logistic regression that predicts the probability of a measurement being taken on mars from the weight:

```{r}
# add code
```


**Task**: generate the ROC curve for this model:

```{r}
# add code
```


# Inference

Back to linear regression now...

## Interval estimation

**Task**: Compute, visualize, and interpret a 95% confidence interval for the slope of the regression line:


```{r}
# add code
```


## Hypothesis testing

**Task**: Test the following hypotheses at the 5% level:

$$
\begin{aligned}
H_0&:\beta_1=0\\
H_A&:\beta_1\neq0
\end{aligned}
$$

```{r}
# add code
```

**Task**: Test the following hypotheses at the 5% level:

$$
\begin{aligned}
H_0&:\beta_1=0.41\\
H_A&:\beta_1\neq0.41
\end{aligned}
$$

# BONUS: regression through the origin
